Title

### 2020-12-10 documents/DraftReport.Rmd
Added references to lit cited

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

Besbeas P., Borysiewicz R.S., Morgan B.J., 2009. Completing the Ecological Jigsaw. In: Thomson D.L., Cooch E.G., Conroy M.J. (eds) Modeling Demographic Processes In Marked Populations. Environmental and Ecological Statistics, vol 3. Springer, Boston, MA. https://doi.org/10.1007/978-0-387-78151-8_22

Besbeas, P., Freeman, S.N., Morgan, B.J.T., Catchpole, E.A., 2002. Integrating mark-recapture-recovery and census data to estimate animal abundance and demographic parameters. Biometrics 58, 540–547.

Besbeas, P., Freeman, S.N., Morgan, B.J.T., 2005. The potential of integrated population modelling. Australian & New Zealand Journal of Statistics 47, 35-48. https://doi.org/10.1111/j.1467-842X.2005.00370.x

@@

Brooks S.P., King R., Morgan B.J.T., 2004. A Bayesian approach to
combining animal abundance and demographic data. Animal
Biodiversity and Conservation 27, 515–529.

@@

Cruz, J., Windels, S.K., Thogmartin, W.E., Crimmins, S.M., Grim, L.H., Zuckerberg, B., 2018. Managing individual nests promotes population recovery of a top predator. Journal of Applied Ecology 55, 1418–1429.

@@

Gamelon, M., Baubet, E., Besnard, A., Gaillard, J.-M., Lebreton, J.-D., Touzot, L., Veylit, L., Gimenez, O., 2019.Efficient use of harvest data: An integrated population model for exploited animal populations. bioRxiv 776104. doi: https://doi.org/10.1101/776104

Lee, A.M., Bjørkvoll, E.M., Hansen, B.B., Albon, S.D., Stien, A., Sæther, B.‐E., Engen, S., Veiberg, V., Loe, L.E., Grøtan, V., 2015. An integrated population model for a long‐lived ungulate: more efficient data use with Bayesian methods. Oikos 124, 806-816. https://doi.org/10.1111/oik.01924

@@

Mormede, S., Parker, S.J., Pinkerton, M.H., 2020. Comparing spatial distribution modelling of fisheries data with single-area or spatially-explicit integrated population models, a case study of toothfish in the Ross Sea region.
Fisheries Research 221, 105381. https://doi.org/10.1016/j.fishres.2019.105381

Oppel, S., Hilton, G., Ratcliffe, N., Fenton, C., Daley, J., Gray, G., Vickery, J., Gibbons, D., 2014. Assessing population viability while accounting for demographic and environmental uncertainty. Ecology 95, 1809–1818.

@@

Schaub, M., Abadi, F., 2011. Integrated population models: A novel analysis framework for deeper insights into population dynamics. Journal of Ornithology 152:S227–S237.

@@

Schaub, M., Gimenez, O., Sierro, A., Arlettaz, R., 2007. Use of Integrated Modeling to Enhance Estimates of Population Dynamics Obtained from Limited Data. Conservation Biology 21, 945-955. https://doi.org/10.1111/j.1523-1739.2007.00743.x

@@

Véran, S., Lebreton, J.D., 2008. The potential of integrated modelling in conservation biology: A case study of the black‐footed albatross (Phoebastria nigripes). Can J Statistics, 36, 85-98. https://doi.org/10.1002/cjs.5550360109

@@

Woodworth, B., Wheelwright, N., Newman, A., Schaub, M., Norris, D.R., 2017. Winter temperatures limit population growth rate of a migratory songbird. Nat Commun 8, 14812. https://doi.org/10.1038/ncomms14812

Zipkin, E.F., Saunders, S.P., 2018. Synthesizing multiple data types for biological conservation using integrated population models. Biological Conservation 217, 240–250.
